---
title: "Week 3 exercises"
format: html
---

## Load the Data and the Libraries

```{r}
library(palmerpenguins)
library(tidyverse)

head(penguins)
```

## Make Your Own Visualization

Pick 2 or 3 variables to plot from the `penguins` dataset and a geometry function. Make sure that you are mapping the right aesthetics to your variables. For example, `color` usually wants a discrete categorical variable such as `species`.

```{r}
library(palmerpenguins)
ggplot(penguins) +
  aes() +
  geom_

```

Try adding any of the following customizations to your above plot. 

- `ggtitle("Palmer penguins are beautiful")`
- `theme_minimal()`
- `theme(axis.text = element_text(angle = 90))`

## Why isn't this working?

This code isn't working like we expect it to work. What do we need to do to fix it?

Hint: we need to map `species` to a different aesthetic. Take a look at `geom_bar()` and see if you can fix it.

```{r}
ggplot(penguins) +
  aes(x = bill_depth_mm,
      color = species) +
  geom_bar()
```
Solution: we need to map `fill` instead of `color`:

```{r}
ggplot(penguins) +
  aes(x = bill_depth_mm,
      fill = species) +
  geom_bar()
```

## Try a new geom

Try out one of the following geoms:

- `geom_hex()`
- `geom_smooth()`
- `geom_violin()`

And try to map the penguins data in and make a plot. Pay attention to the data types and whether it makes sense to map.

Facet your plot by either `species` or `island`. Are there any unexpected findings?

```{r}
ggplot(penguins) +
  aes(y=bill_length_mm,
      x=species,
      fill=species) +
  geom_violin() +
  facet_wrap(~island)
```


## `geom_tile()` + `geom_text()` = heatmap

Why is this heatmap missing boxes? Hint: look at penguin counts.

Look at the `count()` function and see if there's an argument we can set to fill in the missing boxes.

```{r}
penguin_counts <- count(x=penguins, species, island)

penguin_counts

ggplot(penguin_counts) +
  aes(x=species, y=island, fill=n) +
  geom_tile() +
  geom_text(aes(label=n), 
            color="white")
```

Solution: we need to set the `.drop=FALSE` in the `count()` function:

```{r}
penguin_counts <- count(x=penguins, species, island, .drop = FALSE)

penguin_counts

ggplot(penguin_counts) +
  aes(x=species, y=island, fill=n) +
  geom_tile() +
  geom_text(aes(label=n), 
            color="white")
```

## `{visdat}` for getting an overview of the data

One of my favorite first visualizations of a dataset is using the `{visdat}` package. Try adding `facet=species`. What does it do?

```{r}
library(visdat)
vis_dat(penguins)
```

Try out the `vis_miss()` function. What does it do?

```{r}
vis_miss(penguins)
```

## Try out `ggplot()` with other data!

```{r}


```