---
title: "Week 3 classwork"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(palmerpenguins)
library(esquisse)
```

## Histogram

What does the `bins` argument do? Try adjusting it and see what happens.

```{r}
ggplot(penguins)  + 
  aes(x = bill_length_mm) + 
  geom_histogram(bins = 10) + 
  theme_bw()
```

## Bar Plot

```{r}
ggplot(penguins) + 
  aes(x = species) + 
  geom_bar()
```

```{r}
ggplot(penguins) + 
  aes(x = species,
      fill = island) + 
  geom_bar()
```

```{r}
ggplot(penguins) + 
  aes(x = species,
      fill = island) + 
  geom_bar()
```

### Looking at Proportions

```{r}
ggplot(penguins) + 
  aes(x = species,
      fill = island) + 
  geom_bar(position = "fill")
```

### Looking at separate bars

```{r}
ggplot(penguins) + 
  aes(x = species,
      fill = island) + 
  geom_bar(position = "dodge")
```

## Scatterplot

### Boring Scatterplot

```{r}
ggplot(penguins) + 
  aes(x = bill_length_mm,
      y = bill_depth_mm) + 
  geom_point()
```

### Colorful Scatterplot

```{r}
ggplot(penguins) + 
  aes(x = bill_length_mm, 
      y = bill_depth_mm,
      color = island) + 
  geom_point() 
```

### Faceted scatterplot

```{r}
ggplot(penguins) + 
  aes(x = bill_length_mm, 
      y = bill_depth_mm, 
      color = island) +
  geom_point() + 
  facet_wrap(~species)
```

## geom_line() and the group aesthetic

```{r}
ggplot(penguins) + aes(x = bill_length_mm, y = bill_depth_mm, color = island, group=island) + geom_line()
```

## Box Plot

Try playing around with the labels in the following plot, adding a observation such as "Penguins have deep bills".

```{r}
ggplot(penguins) +
  
  aes(x = species, 
      y = bill_depth_mm, 
      fill=species) + 
  
  geom_boxplot() + 
  
  labs(x = "Species", 
       y = "Bill Depth (mm)", 
       title = "Figure 1")

```

## Esquisse...

```{r}
esquisser(penguins)
```

## Another View of `ggplot2`

Try out the first two chapters of the `R-Bootcamp` <https://r-bootcamp.netlify.app>